\documentclass[a4paper,12pt]{article}

% Setting up page geometry
\usepackage[margin=1in]{geometry}

% Including essential packages for document formatting
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}

% Configuring section title formats
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

% Setting up font
\usepackage{times}

\begin{document}

\begin{center}
    \textbf{\Large GDPR Consent Form for Data Processing in User Study}
\end{center}

\vspace{0.5cm}

\begin{center}
    \textbf{Study Title:} Interactive Debugging of LLM Agents for Software Development – Usability and Utility Evaluation
\end{center}

\vspace{0.5cm}

\textbf{Data Controller:} XXX \\
\textbf{Institution:} XXX \\
\textbf{Contact:} XXX \\

\textbf{Participant's Name:} \underline{\hspace{5cm}} (to be filled in by participant) \\
\textbf{Participant Key:} \underline{\hspace{5cm}} (to be filled in by participant)

\rule{\textwidth}{0.4pt}

\section{Purpose of This Form}

In accordance with the General Data Protection Regulation (GDPR) and the German Federal Data Protection Act (BDSG), this form provides information about the personal data we will collect, process, and store as part of the user study. It explains the purpose and legal basis for data processing, your rights as a data subject, and how you can withdraw consent. Your participation and provision of personal data are entirely voluntary, and you may withdraw your consent at any time without negative consequences.

\section{Data Processing Information}

\subsection{Data Controller and Contact Details}

The data controller responsible for processing your personal data is: \\
XXX

\subsection{Purpose and Legal Basis for Data Processing}

We collect and process your personal data for the purpose of organizing, conducting, and evaluating the results of the user study titled ``Interactive Debugging of LLM Agents for Software Development – Usability and Utility Evaluation.'' The legal basis for processing is your explicit consent under Article 6(1)(a) GDPR.

\subsection{Data Collected}

For the purpose of organizing, conducting, and evaluating the study, we will collect the following personal data:
\begin{itemize}
    \item Email address (for correspondence, and, if opted, to send feedback on task results)
    \item Age range (18--24, 25--34, 35--44, 45+)
    \item Gender
    \item Current occupation
    \item Technical experience
\end{itemize}

During the study, we will collect the following additional data:
\begin{itemize}
    \item Answers provided to the tasks
    \item Completion time for each task
    \item Answers provided in the NASA Task Load Index (TLX) questionnaires
    \item Answers provided in the feedback form relating to our software
\end{itemize}

All participants will be assigned a unique participant key, which cannot be used to determine your personal identity. This key will be used to anonymize your data during analysis and reporting.

\subsection{Use and Publication of Data}

We reserve the right to publish the individual results and participant information (age range, gender, current occupation, technical experience, task answers, and completion times) identified solely by the participant key, ensuring anonymity. Your email address will not be published or shared.

If you opt to receive feedback on your task performance, your email address will be used to send you a report summarizing the study results at a later date, after data evaluation.

\subsection{Data Storage and Retention}

Your personal data will be stored securely and accessible only to authorized personnel involved in the study. Data will be retained only for as long as necessary to fulfill the purposes outlined (e.g., study evaluation and publication). Anonymized data (linked to the participant key) may be retained indefinitely for research purposes. Personal data, including email addresses, will be deleted no later than 3 months.

\subsection{Data Sharing}

Your personal data will not be shared with third parties. Any data shared will be anonymized using the participant key.

\subsection{Your Rights as a Data Subject}

Under the GDPR, you have the following rights regarding your personal data:
\begin{itemize}
    \item \textbf{Right to access} (Article 15): You may request access to your personal data and information about how it is processed.
    \item \textbf{Right to rectification} (Article 16): You may request correction of inaccurate or incomplete data.
    \item \textbf{Right to erasure} (Article 17): You may request deletion of your personal data (``right to be forgotten'').
    \item \textbf{Right to restriction of processing} (Article 18): You may request restriction of data processing under certain conditions.
    \item \textbf{Right to data portability} (Article 20): You may request your data in a structured, commonly used, and machine-readable format.
    \item \textbf{Right to object} (Article 21): You may object to the processing of your data.
    \item \textbf{Right to withdraw consent} (Article 7(3)): You may withdraw your consent at any time without affecting the lawfulness of processing prior to withdrawal.
\end{itemize}

To exercise these rights, contact the data controller listed above. You also have the right to lodge a complaint with a supervisory authority, such as XXXX.

\subsection{Withdrawal of Consent}

You may withdraw your consent to data processing at any time by contacting the data controller listed above. Withdrawal will not affect the lawfulness of processing based on consent before its withdrawal. Upon withdrawal, we will cease processing your personal data and delete it, unless required for legal or research purposes (in anonymized form).

\section{Consent}

I have read and understood the information provided in this form regarding the collection, processing, and storage of my personal data. I have had the opportunity to ask questions, and any questions have been answered to my satisfaction.

I voluntarily consent to the collection and processing of my personal data as described above for the purposes of organizing, conducting, and evaluating the user study. I understand that I may withdraw my consent at any time without negative consequences by contacting the data controller.

I confirm that I am at least 18 years old and capable of providing informed consent under German law.

\vspace{0.5cm}

\textbf{Date:} \\

\textbf{Participant's Signature:} \underline{\hspace{5cm}}


\end{document}